---
title: "R Notebook"
output: html_notebook
---

```{r}
library(CodeClanData)
library(tidyverse)
```


1.

```{r}
drinks_content
View(drinks_content)
dim(drinks_content)
ncol(drinks_content)
nrow(drinks_content)
names(drinks_content)
```
a mix of double and character data types

2.
```{r}
drinks_content %>% 
  select(Beverage_category, Beverage, Beverage_prep, Calories) %>% 
  filter(!is.na(Calories))
```

3.

```{r}
drinks_content %>% 
  mutate(calorie_diff = Calories - 135) %>% 
  select(Beverage_category:Calories)
```

4. Most of the beverage categories average between 100-300 calories, with one outlier of 'coffee' having an average of ~4 calories.
'Coffee' has the lowest calorie count and smoothies and frappucinno's have the highest calorie counts.

```{r}
drinks_content %>% 
  group_by(Beverage_category) %>% 
  summarise(avg_calories = mean(Calories))

# Highest 3 by mean calories
drinks_content %>% 
  group_by(Beverage_category) %>% 
  summarise(avg_calories = mean(Calories)) %>% 
  arrange(desc(avg_calories)) %>% 
  head(3)

# Lowest 3 by mean calories
drinks_content %>% 
  group_by(Beverage_category) %>% 
  summarise(avg_calories = mean(Calories)) %>% 
  arrange(avg_calories) %>% 
  head(3)
```

5.The beverage prep types average between 5-300 calories.
Solo and Doppio have the lowest calorie counts and Whole Milk and Venti Nonfat Milk have the highest calorie counts.


```{r}
drinks_content %>% 
  group_by(Beverage_prep) %>% 
  summarise(avg_calories = mean(Calories))

# Highest 3 by mean calories
drinks_content %>% 
  group_by(Beverage_prep) %>% 
  summarise(avg_calories = mean(Calories)) %>% 
  arrange(desc(avg_calories)) %>% 
  head(3)

# Lowest 3 by mean calories
drinks_content %>% 
  group_by(Beverage_prep) %>% 
  summarise(avg_calories = mean(Calories)) %>% 
  arrange(avg_calories) %>% 
  head(3)
```

6.

```{r}
avg_calories <- drinks_content %>% 
  summarise(avg_calories = mean(Calories)) %>% 
  pull(avg_calories)

drinks_content %>% 
  group_by(Beverage_prep) %>% 
  summarise(mean_calories = mean(Calories)) %>% 
  filter(mean_calories > avg_calories)
```

```{r}
# Forgive me for this, I wanted to see how bad it could get without variables or %>% 
# This took longer than the rest of the homework combined.
filter(summarise(group_by(drinks_content, Beverage_prep), mean_calories = mean(Calories)), mean_calories  > pull(summarise(drinks_content, avg_calories = mean(Calories)), avg_calories))
```



7.A Short Brewed Coffee, which is Coffee, has the fewest calories of any 'Coffee', having 3 calories.

```{r}
drinks_content %>% 
  filter(Beverage_category == "Coffee") %>% 
  select(Beverage_category, Beverage, Beverage_prep, Calories) %>% 
  arrange(Calories) %>% 
  head(1)
```

