---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(dplyr)
library(readr)
library(stringr)
```

```{r}
books <- read_csv("data/books.csv")

books
```

```{r}
#view(books)
```

```{r}
#dim(books)
#names(books)
#glimpse(books)
```

```{r}
books %>% 
  summarise(across(.cols = everything(), .fns = ~sum(is.na(.))))
```

```{r}
books_with_pages <- books %>% 
  filter(num_pages > 0)
```



```{r}
books %>% 
  distinct(language_code)
```

Finds the average rating of all books.
```{r}
books_with_pages %>% 
  select(title, average_rating) %>% 
  summarise(avg_avg_rating = mean(average_rating))
```

Finds the average rating of each language.
```{r}
books_with_pages %>% 
  group_by(language_code) %>% 
  summarise(avg_avg_rating = mean(average_rating)) %>% 
  arrange(desc(avg_avg_rating))
```

Finds the average rating of each variety of English.
```{r}
books_with_pages %>% 
  group_by(language_code) %>% 
  filter(str_detect(language_code, "en")) %>% 
  summarise(avg_avg_rating = mean(average_rating)) %>% 
  arrange(desc(avg_avg_rating))
```

Finds the average rating of books in English.
```{r}
books_with_pages %>% 
  filter(str_detect(language_code, "en")) %>% 
  summarise(avg_avg_rating = mean(average_rating)) %>% 
  pull(avg_avg_rating)
```

Finds the average rating of books not in English.
```{r}
books_with_pages %>% 
  filter(!str_detect(language_code, "en")) %>% 
  summarise(avg_avg_rating = mean(average_rating)) %>% 
  pull(avg_avg_rating)
```

Finds the number of books with a rating of 0.
```{r}
books %>% 
  filter(average_rating == 0) %>% 
  summarise(n = n()) %>% 
  pull(n)
```

```{r}
books %>% 
  filter(text_reviews_count == 0 &
           average_rating == 0) %>% 
  summarise(n = n()) %>% 
  pull(n)
```


Finds the average rating for languages with more than a single book.
```{r}
books_with_pages %>% 
  group_by(language_code) %>% 
  filter(n() > 1) %>% 
  summarise(avg_avg_rating = mean(average_rating)) %>% 
  arrange(desc(avg_avg_rating))
```


Finds the average number of pages.
```{r}
books_with_pages %>% 
  summarise(avg_pages = mean(num_pages))
```

Finds the average number of pages for each language.
```{r}
books_with_pages %>% 
  group_by(language_code) %>% 
  summarise(avg_pages = mean(num_pages)) %>% 
  arrange(desc(avg_pages))
```

Finds the number of books for each language.
```{r}
books %>% 
  group_by(language_code) %>% 
  summarise(n = n())
```

Finds the number of books in English and the number of books not in English.
```{r}
books %>% 
  filter(str_detect(language_code, "en")) %>% 
  summarise(n = n()) %>% 
  pull(n)

books %>% 
  filter(!str_detect(language_code, "en")) %>% 
  summarise(n = n()) %>% 
  pull(n)
```
Finds the books with no pages.
```{r}
books %>% 
  filter(num_pages == 0) %>% 
  select(title)
```


## Summary of findings

There are 76 books listed with a page count of 0, which have been discounted from
most checks.
A vast majority of the books listed are in English, with the non-English books
having a slightly higher average rating.
The highest average rating for a language is Welsh, with the lowest nonzero average
rating being for Galician.
If languages with only one listed book are removed, the highest rated language
is Chinese, and the lowest rated is Swedish.
Canadian English is the highest rated English and middle English is the lowest.
25 books have an average rating of 0, which is unlikely but still possible if it's
a really bad book. 24 of these have no text reviews.
Middle English has the highest average page count and Welsh has the lowest.