---
title: "Fergus Cherry Data Analysis Homework Day 3"
output: html_notebook
---

```{r}
library(tidyverse)
library(dplyr)
library(CodeClanData)
library(janitor)
library(readr)
library(skimr)
```

```{r}
movies = read_csv("data/movies.csv")
#view(movies)
```

```{r}
skim(movies)
```

## MVP

1. 7 character columns, 6 numeric columns
2 missing runtime values are probably publicly available and could be added
1 missing release date also could probably be found
the missing homepage, overview and tagline values can be ignored when evaluating the numeric values of thos entries.
could compare average budgets, revenues and popularities for various language groups
could compare how budget correlates with revenue and popularity
could check if revenue compares with popularity



2.

```{r}
movies %>% 
  select(original_title, title) %>% 
  filter(original_title != title)
```

```{r}
movies_selected <- movies %>% 
  select(title, runtime, budget)
```

3. 2 missing runtimes, no other missing values

```{r}
movies_selected %>% 
  summarise(across(.cols = everything(), .fns = ~sum(is.na(.))))
```


4.37 have missing or 0 runtime

```{r}
movies_runtime <- movies_selected %>% 
  mutate(runtime = na_if(runtime, 0))
```

```{r}
movies_runtime %>% 
  summarise(sum(is.na(runtime)))
```


5.

```{r}
movies_imputed <- movies_runtime %>% 
  mutate(runtime = coalesce(runtime, mean(runtime, na.rm = TRUE)))

movies_imputed %>% 
  summarise(sum(is.na(runtime)))
```

6.

```{r}
movies_imputed %>% 
  slice_min(order_by  = runtime, n = 10)

movies_imputed %>% 
  slice_max(order_by  = runtime, n = 10)
```

7.

```{r}
movies_imputed <- movies_imputed %>% 
  mutate(budget = if_else(budget < 100, mean(budget), budget))
```



## Extension


1.

```{r}
movie_budgets <- movies_imputed %>% 
  mutate(budget_type = case_when(budget < 12e6 ~ "Small budget",
                                 budget >= 12e6 & budget <= 40e6 ~ "Medium budget",
                                 budget > 40e6 ~ "Big budget"))
```


2.

```{r}
movies %>% 
  summarise(across(where(is.character), ~sum(is.na(.))))
```
# For if only `NA` values count as missing
```{r}
movies %>% 
  summarise(across(where(is.numeric), ~sum(is.na(.))))
```

# For if 0 as runtime values count as missing but budget as 0 is ok
```{r}
movies %>% 
  mutate(runtime = na_if(runtime, 0)) %>% 
  summarise(across(where(is.numeric), ~sum(is.na(.))))
```

# For if 0 as runtime or budget values count as missing
```{r}
movies %>% 
  mutate(runtime = na_if(runtime, 0),
         budget = na_if(budget, 0)) %>% 
  summarise(across(where(is.numeric), ~sum(is.na(.))))
```


# For if 0 as runtime values and budget values less than 100 count as missing
```{r}
movies %>% 
  mutate(runtime = na_if(runtime, 0),
         budget = if_else(budget < 100, NA, budget)) %>% 
  summarise(across(where(is.numeric), ~sum(is.na(.))))
```

